Transportation network with multiple lines

### 2022-04-05 multiple_lines/notes/latex/Notes_trajet.tex
update notes and began prototyping functions

The $(n \times n)$ \emph{origin-destination matrix}, denoted by $\mathbf{N} = (n_{st})$, $n_{st} \geq 0, \; \forall s,t$, contains the flow (e.g. the number of passengers) entering the network in source node $s$ and leaving it in target node $t$. We can denote its margins with 
\begin{align}
\bm{\sigma}_\text{in} := \mathbf{N} \mathbf{e}_n \\
\bm{\sigma}_\text{out} := \mathbf{N}^\top \mathbf{e}_n
\end{align}
where $\mathbf{e}_n$ is the vector of ones of size $n$. The vector $\bm{\sigma}_\text{in} = (\sigma^\text{in}_i)$ is the \emph{vector of flow entering the network} and $\bm{\sigma}_\text{in} = (\sigma^\text{in}_i)$ is the \emph{vector of flow escaping the network}. We have
\begin{equation}
\sigma^\text{in}_{\bullet} = \sigma^\text{out}_{\bullet}.
\end{equation}

@@

A flow on edges is represented by the $(n \times n)$ \emph{flow matrix} $\mathbf{X} = (x_{ij})$, verifying
\begin{align}
x_{ij} &\geq 0, \qquad \forall i,j, \\
a_{ij} = 0 &\Rightarrow x_{ij} = 0, \qquad \forall i,j, \\ 
x_{i\bullet} + \sigma^\text{in}_i &= x_{\bullet i} + \sigma^\text{out}_i, \qquad \forall i.
\end{align}
Again, we can decompose the flow matrix with 
\begin{equation}
\mathbf{X} = \mathbf{X}_\text{W} + \mathbf{X}_\text{B} \qquad \mathbf{X}_\text{W} := \sum_{k=1}^l \mathbf{X}_k
\end{equation}
where $\mathbf{X}_k$ represent the flow inside line $k$, $\mathbf{X}_\text{W}$ is the flow inside all lines, and $\mathbf{X}_\text{B}$ the flow between lines. This decomposition allows us to define 
the \emph{vector of flow entering lines} $\bm{\rho}_\text{in} = (\rho^\text{in}_i)$ and the \emph{vector of flow escaping lines} $\bm{\rho}_\text{out} = (\rho^\text{out}_i)$, with
\begin{align}
\bm{\rho}_\text{in} &:= \bm{\sigma}_\text{in} + \mathbf{X}^\top_\text{B} \mathbf{e}_n, \\
\bm{\rho}_\text{out} &:= \bm{\sigma}_\text{out} + \mathbf{X}_\text{B} \mathbf{e}_n,
\end{align}
where $\mathbf{e}_n$ is the vector of ones of size $n$. It is easy to see that we still have $\rho^\text{in}_\bullet = \rho^\text{out}_\bullet$. \\

>>>>

The $(n \times n)$ \emph{origin-destination matrix}, denoted by $\mathbf{N} = (n_{st})$, $n_{st} \geq 0, \; \forall s,t$, contains the flow (e.g. the number of passengers) entering the network in source node $s$ and leaving it in target node $t$. We can denote its margins with 
\begin{align}
\bm{\sigma}_\text{in} := \mathbf{N} \mathbf{e}_n \\
\bm{\sigma}_\text{out} := \mathbf{N}^\top \mathbf{e}_n
\end{align}
where $\mathbf{e}_n$ is the vector of ones of size $n$. The vector $\bm{\sigma}_\text{in} = (\sigma^\text{in}_i)$ is the \emph{vector of flow entering the network} and $\bm{\sigma}_\text{in} = (\sigma^\text{in}_i)$ is the \emph{vector of flow leaving the network}. We have
\begin{equation}
\sigma^\text{in}_{\bullet} = \sigma^\text{out}_{\bullet}.
\end{equation}

@@

A flow on edges is represented by the $(n \times n)$ \emph{flow matrix} $\mathbf{X} = (x_{ij})$, verifying
\begin{align}
x_{ij} &\geq 0, \qquad \forall i,j, \\
a_{ij} = 0 &\Rightarrow x_{ij} = 0, \qquad \forall i,j, \\ 
x_{i\bullet} + \sigma^\text{in}_i &= x_{\bullet i} + \sigma^\text{out}_i, \qquad \forall i.
\end{align}
Again, we can decompose the flow matrix with 
\begin{equation}
\mathbf{X} = \mathbf{X}_\text{W} + \mathbf{X}_\text{B} \qquad \mathbf{X}_\text{W} := \sum_{k=1}^l \mathbf{X}_k
\end{equation}
where $\mathbf{X}_k$ represent the flow inside line $k$, $\mathbf{X}_\text{W}$ is the flow inside all lines, and $\mathbf{X}_\text{B}$ the flow between lines. This decomposition allows us to define 
the \emph{vector of flow entering lines} $\bm{\rho}_\text{in} = (\rho^\text{in}_i)$ and the \emph{vector of flow leaving lines} $\bm{\rho}_\text{out} = (\rho^\text{out}_i)$, with
\begin{align}
\bm{\rho}_\text{in} &:= \bm{\sigma}_\text{in} + \mathbf{X}^\top_\text{B} \mathbf{e}_n, \\
\bm{\rho}_\text{out} &:= \bm{\sigma}_\text{out} + \mathbf{X}_\text{B} \mathbf{e}_n,
\end{align}
where $\mathbf{e}_n$ is the vector of ones of size $n$. It is easy to see that we still have $\rho^\text{in}_\bullet = \rho^\text{out}_\bullet$. \\
